Synthesizing Symmetric Lenses

### 2018-07-11 papers/SymmetricLenses/main.tex
clarification on first sentence of eval

% begin evaluation
\section{Evaluation}
\label{sec:evaluation}
We have implemented our symmetric DNF lenses and the synthesis of them as an
extension to Boomerang. We added symmetric lens combinators to Boomerang, and
implemented all of Boomerang's asymmetric lens combinators using a combination of
the symmetric lens combinators, as well as other symmetric lens combinators for
the asymmetric theory extensions present in Boomerang, like matching lenses and
quotient lenses. We also integrated our synthesis engine into Boomerang. It allows users to write synthesis tasks
alongside lens combinators, use those synthesis results in the manual writing of
new lenses, and use previously defined lenses in the synthesis of new lenses.

>>>>

% begin evaluation
\section{Evaluation}
\label{sec:evaluation}
We have implemented our symmetric DNF lenses and the synthesis of them as an
extension to Boomerang. We added symmetric lens combinators to Boomerang, and
implemented all of Boomerang's asymmetric lens combinators 
using a combination of the symmetric lens combinators presented in this
paper and symmetric versions of the asymmetric theory extensions
already present in Boomerang, like matching lenses and quotient lenses.
We also integrated our synthesis engine into Boomerang. It allows users to write synthesis tasks
alongside lens combinators, use those synthesis results in the manual writing of
new lenses, and use previously defined lenses in the synthesis of new lenses.
